\huge FOVEROS Chess Engine\\\Large (Modelling 2)

### 2014-11-28 Draft Final 1.tex
My changes

Chess engines adopt a brute for approach. Therefore, development of chess engines tie together a broad range of topics, improve the understanding of tree searching algorithms and its optimisations, logical thought processes behind the game as well as a deeper understanding of computational thought and Artificial Intelligence(AI).

@@

@@

\subsection{Tuning}
\indent\indent Tuning is the process of finding the optimum gains for the different scores in the Heuristics Analysis function. The different gains increase or decrease the effect of different parameters on the board score. Tuning is a difficult process because the values are relative and therefore trial and error is to be used to determine the optimum value. By comparison, the programmers of the legendary Deep Blue machine had made plausible initial guesses for values and there was a lot of uncertainty to what the correct values should be.\cite{chess5}

@@

@@

>>>>

Chess engines adopt a brute for approach. Therefore, development of chess engines tie together a broad range of topics, such as tree searching algorithms and its optimisations, logical thought processes behind the game as well as a deeper understanding of computational thought and Artificial Intelligence(AI).

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{HeuristicProblem}
\caption{Rook Does Not Seperate From King}
\label{fig:chess1}
\end{figure}

@@

\subsection{Tuning \& Resulting AI Behaviour}
\indent\indent Tuning is the process of finding the optimum gains for the different scores in the Heuristics Analysis function. The different gains increase or decrease the effect of different parameters on the board score. Tuning is a difficult process because the values are relative and therefore trial and error is to be used to determine the optimum value. By comparison, the programmers of the legendary Deep Blue machine had made plausible initial guesses for values and there was a lot of uncertainty to what the correct values should be.\cite{chess5}

@@

	$Fig.$ 21 shows an interesting scenario in the situation of AI vs AI. This is where castling for Black has taken place in the late game and White has only 2 pieces left. Black makes repetitive moves for the Bishop and does not choose to seperate the Rook and King. As seen on the graph, Black's score stagnates as a result. This problem is a result of the Heuristics function where pieces in the castling position are given a higher score and because the board score is a linear calculation of summing up different contributions, any other contribution will not be as high as the castling position. This is the weakness of the linear scoring function. A simple mitigation to this problem is to add a random gain to the castling score. A more complex mitigation will be to look into dynamic scoring functions that take into account game stage and situations.

@@

	The Heuristic Analysis function is proven to be simple and has more room for improvement. Dynamic scoring can be introduced to take into account more factors such as game stage and situations as well as decrease the impact of having pieces that are less valuable in the late game.
